Surrogate Modelling of the Tritium Breeding Ratio

### 2020-06-21 talk_ucl_cdt_200622/adaptive.tex
improve toy theory slide typesetting

\begin{frame}
	\frametitle{Application on Toy Theory}
	\begin{itemize}
		\item % TODO
	\end{itemize}
\end{frame}

>>>>

\begin{frame}
	\frametitle{Application on Toy Theory}
	Toy functional TBR theory with wavenumber n, and similar ANN performance to Paramak:
	\begin{align*}
		\text{TBR} = \frac{1}{|C|}\sum_{i \in C} \left[1 + \sin(2\pi n (x_i - 1/2)) \right]
	\end{align*}

	\vspace{1em}

	\begin{columns}[T]
		\column{0.5\paperwidth}
		\vspace{0.5em}
		Evaluation performed both on the adaptively-sampled dataset and on a baseline uniform-random dataset.\newline

		An baseline scheme with incremental but uniform-random samples used as a placebo comparison.

		\column{0.4\paperwidth}
		\includegraphics[width=0.4\paperwidth]{sintoy}

\begin{frame}
    \frametitle{Adaptive Sampling: Results}

    \begin{center}
    \includegraphics[width=12cm]{qassresult}
    \end{center}

\end{frame}
